% TODO: fix indentation
\documentclass{article}
\usepackage{amsmath}
\usepackage{titlesec}
\renewcommand{\thesubsection}{\thesection.\alph{subsection}} %Follow hw's notation
\renewcommand{\thesubsubsection}{\thesubsection.\alph{subsubsection}} %Follow book's notation
\titleformat{\section}{\normalfont\Large}{\thesection}{1em}{} %Remove bold font
\titleformat{\subsection}{\normalfont\large}{\thesubsection}{1em}{} %Remove bold font
\titleformat{\subsubsection}[runin]{\normalfont\normalsize}{\thesubsubsection}{1em}{} %Remove bold font and make it runin
\title{MATH 545: Homework 1}
\author{Yingli, Laurette, Fernando}
\date{September 13, 2023}
\begin{document}
\maketitle
\section{Solve the following ODEs}
\subsection{$(y')^2 -4y +4 = 0$}

\textbf{Solution:}

		We proceed by separation of variables.
		\begin{align*}
			(y')^2 -4y +4 = 0 \Longrightarrow (y')^2 = 4y -4. %Merge them in the same line
		\end{align*}
		This means that we have two options for $y'$, namely:
		\[y' = \pm 2\sqrt{y-1}.\]
%Change an expression
	Then, we separate variables,
	\[ \frac{dy}{dx} = \pm 2\sqrt{y-1} \implies \pm\frac{dy}{ 2\sqrt{y-1}} = dx.\]
		Integrating both sides simultaneously, we get:
		\[\pm \sqrt{y-1} = x+c,\]

		then
		\begin{equation} \label{sol}
			y = (x+c)^2 + 1.
		\end{equation}
		Now we test the function we found. First we notice that
		\begin{equation} \label{sol_deriv}
			y' = 2(x+c),
		\end{equation}
		then we substitute (\ref{sol}) and (\ref{sol_deriv}) in the original equation to obtain
		%\begin{align*}
		%	(2(x+c))^2 -4((x+c)^2 + 1) +4 =0 \\
		%	\iff 4(x+c)^2 -4(x+c)^2 -4 + 4 =0,
		%\end{align*}
%Change some details
		\[ [2(x+c)]^2 -4[(x+c)^2 + 1] +4= 4(x+c)^2 -4(x+c)^2 -4 + 4 =0,\]
		so the function we found is in fact a solution.

\subsection{$(y\;\text{sin} x + xy\;\text{cos}x)dx + (x\;\text{sin}x + 1)dy = 0$}

\textbf{Solution:}
		
		We start by showing that this equation is exact.

		In this case, we have   
%change layout
		\begin{equation*}
			\begin{cases}
				M(x,y) = y\text{sin}x + xy\text{cos}x,
				\\
				N(x,y) = x\text{sin}x + 1.
			\end{cases}
		\end{equation*}
	
%change layout
		Then
		\begin{equation*}
			\begin{cases}
				\frac{\partial M(x,y)}{\partial y} = \text{sin}x + x\text{cos}x,
				\\
				\frac{\partial N(x,y)}{\partial x} = \text{sin}x + x\text{cos}x.
			\end{cases}
		\end{equation*}
		
		
	
		i.e. \[ \frac{\partial M(x,y)}{\partial y} = \frac{\partial N(x,y)}{\partial x}.\]

		Hence, the equation is exact.

		Now, we solve $\frac{\partial f(x,y)}{\partial y} = x\text{sin}x + 1$. 
		Integrating with respect to $y$, we get
		\[f(x,y) = y(x\text{sin}x +1) + h(x).\]
		In order to determine $h(x)$, we differentiate with
		respect to $x$ to obtain
		\[\frac{\partial f(x,y)}{\partial x} = y(\text{sin}x+x\text{cos}x) + h'(x).\]
		This must be equal $M(x,y)$, so:
		\[y(\text{sin}x+x\text{cos}x) + h'(x) = y\text{sin}x + xy\text{cos}x,\]
		this implies that $h'(x)=0$, which means that $h(x) = c_1$.
		
		So the solution is implicitly given by:
		%\begin{align*}
		%	f(x,y) = y(x\text{sin}x +1) + c_1 = c_2 \\
		%	\iff y(x\text{sin}x +1) = c. \\
		%\end{align*}
%Change some detail
		\[ f(x,y) = y(x\text{sin}x +1) + c_1 = c_2 \implies y(x\text{sin}x +1) = c.\]
		In order to verify that this function solves the equation we calculate the differential,
  %change layout     
		\begin{equation*}
			\begin{cases}
				\frac{\partial f}{\partial x} = y\text{sin}x + xy\text{cos}x,
				\\
				\frac{\partial f}{\partial y} = x\text{sin}x + 1.
			\end{cases}
		\end{equation*}

		
		So when we calculate $df$, we get:
		\[ df = (y\text{sin}x + xy\text{cos}x)dx + (x\text{sin}x + 1)dy =0.\]
		Hence, this solves the equation.
		
\subsection{$y' + (2/x)y = x$; initial condition $y(1)=0$}

\textbf{Solution:}

		We begin by solving the homogeneous equation

		\[ \frac{dy}{dx} + \frac{2y}{x} = 0.\]

		By separating variables

		\[\frac{dy}{y} = -2\frac{dx}{x} \implies ln(y) = -2ln(x) + c_1 \implies y = \frac{c_2}{x^2}.\]

		Now we set

		\begin{equation} \label{sol_homo}
			y(x) = q(x)u(x),
		\end{equation}

		where $q(x) = \frac{1}{x^2}$. Then, we substitute (\ref{sol_homo}) into the original equation,
       \begin{equation*}
	         \begin{aligned}
	        	x&=y' + (2/x)y \\
	        	&=q'(x)u(x) +q(x)u'(x) + (2/x)q(x)u(x) \\
	        	&=\frac{-2}{x^3}	u(x) +\frac{1}{x^2}u'(x) + (2/x)\frac{1}{x^2}u(x)\\
	        	&=\frac{1}{x^2}u'(x)
	         \end{aligned}
       \end{equation*}
    Therefore, $u'(x) = x^3$, integrating $u'(x)$ with respect to $x$, we obtain:
        \begin{equation}\label{u(x)}
        	u(x) = \frac{x^4}{4} + c .
        \end{equation} 
		Since we know $q(x)$, we can substitute (\ref{u(x)}) into (\ref{sol_homo}) to get:
		\[y(x) = \frac{1}{x^2}\left(\frac{x^4}{4}+c\right) = \frac{x^2}{4} + \frac{c}{x^2}.\]
		The initial condition is $y(1)=0$, thus \[ y(1)=\frac{1}{4} + c= 0 \implies c=-\frac{1}{4},\]
		therefore,
		\[y(x) = \frac{1}{x^2}\left(\frac{x^4}{4}+c\right) = \frac{x^2}{4} - \frac{1}{4x^2}.\]
		Now we check that the function found is a solution.

		Firstly, the initial condition:
		\[y(1)= \frac{1^2}{4} - \frac{1}{4\cdot 1^2} =0.\]

		Secondly, we check that it satisfies the equation.
		\[y'+(2/x)y = \left(\frac{x}{2} + \frac{1}{2x^3}\right) +(2/x)\left(\frac{x^2}{4} - \frac{1}{4x^2}\right) = x.\]
		Hence, the function solves the equation.

% \titleformat{\subsection}{\normalfont\large\bfseries}{\thesubsection}{1em}{}
\section{Strauss section 1.2}
\subsection{Exercise 1}
			Solve the first-order equation
			$2u_t +3u_ x =0$ with the auxiliary condition $u=\text{sin}x$ when $t=0.$

\textbf{Solution:}

			We solved this type of equation in class.
			The solution is 
			\[ u(t,x)=f(2x-3t),\]
			where $f$ is any sufficiently nice function.

			Using the initial condition, we get:
			\[u(0,x)=f(2x)=\text{sin}x,\]
			so $f(x)=\text{sin}\left(\frac{x}{2}\right)$.
			Finally we have:
			\[u(t,x)=\text{sin}\left(x-\frac{3}{2}t\right).\]
			We check it by differentiating,
%Yingli changes the layout
			\begin{equation*}
				\begin{cases}
					u_x=\text{cos}\left(x-\frac{3}{2}t\right),
					\\
					u_t=-\frac{3}{2}\text{cos}\left(x-\frac{3}{2}t\right).
				\end{cases}
			\end{equation*}

			Therefore,
			\[ 2u_t +3u_x=-3\text{cos}\left(x-\frac{3}{2}t\right) + 3\text{cos}\left(x-\frac{3}{2}t\right)=0.\]

			As for the initial condition:
			\[u(0,x)=\text{sin}\left(x-\frac{3}{2}\cdot0\right)=\text{sin}x.\]

			Hence $u(t,x)$ is in fact a solution to the PDE.

		\subsection{Exercise 2}
		Solve the equation $3u_y + u_{xy} =0.$

		\textbf{Solution:}

			Let $v=u_y$, then the equation becomes:
			\[3v+v_x=0.\]
			By separating variables, we get \[\frac{\partial v}{v}=-3\partial x.\]
			Integrating both sides simultaneously, the equation is \[ ln(v) = -3x + f(y),  \]
			Therefore, \[ v = g(y)e^{-3x},\]
			where $g(y)=e^{f(y)}$.
			Since $v=u_y$, we have:
			\[u(x,y)=\int vdy = e^{-3x}\int g(y)dy + h(x).\]
%Yingli adds check part.	
			Then we need to check it.
			\begin{equation*}
				\begin{cases}
					u_{x}=-3e^{-3x}\int g(y)dy + h^{'}(x),
					\\
					u_{y}=e^{-3x} g(y),
					\\
					u_{xy}=-3e^{-3x} g(y).
				\end{cases}
			\end{equation*}
			Therefore, \[3u_y + u_{xy}=3e^{-3x} g(y)-3e^{-3x} g(y)=0.\]
            Hence $u(t,x)$ is the solution of the PDE.


    \subsection{Exercise 6}
	Solve the equation $\sqrt{1-x^2}u_x+u_y=0$ with the condition $u(0, y)=y.$
		
	\textbf{Solution:}

	    The characteristic curve satisfies the ODE:
            \[ \frac{dy}{dx}=\frac{1}{\sqrt{1-x^2}}.\]
			To solve the solution, we separate variables: 		
			\[ dy=\frac{1}{\sqrt{1-x^2}}dx.\]
			By integrating, \[y= arcsinx + c .\]
			Since $u(x,y)$ is a constant on each such curve, so
			\[ u(x,y)=f(c)=f(y - arcsinx).\]
			And the initial condition is $u(0,y)=y$, then $u(0,y)=f(y)=y.$

			Finally we have:
			\[u(t,x)=y - arcsinx.\]
			We check our solution by differentiating:
			\begin{equation*}
				\begin{cases}
					u_x=-\frac{1}{\sqrt{1-x^2}},
					\\
					u_y=1.
				\end{cases}
			\end{equation*}
			Thus, \[\sqrt{1-x^2}u_x+u_y=-\sqrt{1-x^2} \cdot \frac{1}{\sqrt{1-x^2}}+1=0.\]

			Hence, $u(t,x)$ is in fact a solution to the PDE.


		\subsection{Exercise 8}
		Solve $au_x+bu_y+cu=0.$
		
		\textbf{Solution:}

		By using coordinate method. Let 
		\begin{equation*}
			\begin{cases}
				\tilde{x}=ax+by, \\
				\tilde{y}=bx-ay.
			\end{cases}
		\end{equation*}

		Replace all $x$ and $y$ derivatives by $\tilde{x}$ and $\tilde{y}$ derivatives.

		By the chain rule, \[u_x=\frac{\partial u}{\partial x}=\frac{\partial u}{\partial \tilde{x}}\cdot\frac{\partial \tilde{x}}{\partial x}+\frac{\partial u}{\partial \tilde{y}}\cdot\frac{\partial \tilde{y}}{\partial x}=au_{\tilde{x}}+bu_{\tilde{y}},\]
		\[u_y=\frac{\partial u}{\partial y}=\frac{\partial u}{\partial \tilde{x}}\cdot\frac{\partial \tilde{x}}{\partial y}+\frac{\partial u}{\partial \tilde{y}}\cdot\frac{\partial \tilde{y}}{\partial y}=bu_{\tilde{x}}-au_{\tilde{y}}.\]
		Hence,
		\begin{equation*}
			\begin{aligned}
			au_x+bu_y+cu&=
			a\left(au_{\tilde{x}}+bu_{\tilde{y}} \right)+b\left(bu_{\tilde{x}}-au_{\tilde{y}}\right) +cu\\
			&=\left(a^2+b^2\right)u_{\tilde{x}}+cu\\
			&=0.
			\end{aligned}
		\end{equation*}

		We separate variables, \[\frac{\partial u}{u}=-\frac{c}{a^2+b^2}\partial \tilde{x}.\]
		At this point we will introduce the value $k=\frac{c}{a^2+b^2}$ just for convenience.

%Little change, add some describe sentence.
		Integrating both sides we get
		\[
			\ln u = -k\tilde{x} +g(\tilde{y}),
		\]
		then
		\[
		u = f(\tilde{y})e^{-k\tilde{x}},
		\]
		where $f(\tilde{y})=e^{g(\tilde{y})}$.
		Thus, the solution is
		\[
		u = f(bx-ay)e^{-k(ax+by)}.
		\]
		We check our solution by differentiating:
		\[
		u_x= b f'(bx-ay)e^{-k(ax+by)} -ak \cdot e^{-k(ax+by)}f(bx-ay),
		\]
		and
		\[
		u_y= -a f'(bx-ay)e^{-k(ax+by)} -bk \cdot e^{-k(ax+by)}f(bx-ay).
		\]	
		Therefore,
			\begin{multline*}
				au_x+bu_y+cu= \\
				ab f'(bx-ay)e^{-k(ax+by)} -a^2k \cdot e^{-k(ax+by)}f(bx-ay)\\
				-ba f'(bx-ay)e^{-k(ax+by)}-b^2k \cdot e^{-k(ax+by)}f(bx-ay) \\
				+cf(bx-ay)e^{-k(ax+by)} \\
				=0.
			\end{multline*}

\section{Strauss section 1.3}
\subsection{Exercise 4}
		Suppose that some particles which are
			suspended in a liquid medium would be pulled down
			at a constant velocity $V > 0$ by gravity in the
			absence of diffusion. Taking account of the
			diffusion, find the equation for the concentration
			of particles. Assume homogeneity in the horizontal
			directions $x$ and $y$. Let the $z$ axis point upwards.

			\textbf{Solution:}

			Since we are assuming homogeneity in the horizontal
			directions, the concentration $u$ depends only on $z$.
			Let $u(z,t)$ be the concentration. We proceed as the
			book does for diffusion.

			The mass in the region of the fluid contained between
			$z_0$ and $z_1$ is given by:
            \begin{equation*}
				M(t) = \int_{z_0}^{z_1} u(z,t)dz.
			\end{equation*}
			Differentiating the former equation with respect to $t$,
			\begin{equation}\label{change_of_mass}
				\frac{dM}{dt}=\int_{z_0}^{z_1}u_t(z,t)dz.
			\end{equation}

			The mass in this section of the fluid cannot change
			except by flowing in or out if its ends.

			There are two processes that regulate the entrance and
			exit of particles into this region of the fluid.
			The first one is diffusion and the second one is the
			movement of the particles due to gravity acting on
			them.

			For diffusion we have:
			\[\frac{dM_{diffusion}}{dt}=ku_z(z_1,t)-ku_z(z_0,t),\]
			just like the example in the book.

			For the movement of particles due to gravity we have:
			\[\frac{dM_{gravity}}{dt} = Vu(z_1,t) - Vu(z_0,t).\]

			Now the total change in the mass per unit of time is
			the sum of this two components.
			\[\frac{dM}{dt}=\frac{dM_{diffusion}}{dt}+\frac{dM_{gravity}}{dt}.\]
			Inputting equations of $\frac{dM_{diffusion}}{dt} $ and $\frac{dM_{gravity}}{dt} $, we have
            \[\frac{dM}{dt}=ku_z(z_1,t)-ku_z(z_0,t) + Vu(z_1,t) - Vu(z_0,t). \]			
			Combining equation (\ref{change_of_mass}), we get:
			\[\int_{z_0}^{z_1}u_t(z,t)dz= ku_z(z_1,t)-ku_z(z_0,t) + Vu(z_1,t) - Vu(z_0,t).\]
			Differentiating with respect to $z_1$, we obtain:
			\[
				u_t=ku_{zz}+Vu_z.
			\]

		\subsection{Exercise 8}
	For the hydrogen atom, if $ \int \left | u \right |^2 d \vec{x } =1$, at $t=0$, show that the same is true at all later times.
		
	\textbf{Solution:}

		If we want to show that $ \int \left | u \right |^2 d \vec{x } =1$ at all later times, we can show that $\frac{d}{dt}\int \left | u \right |^2 d \vec{x } =0$.
                  
		We begin by noticing that:
		\begin{equation} \label{d|u|^2/dt}
			 \frac{d}{dt} \left | u \right |^2= \frac{d}{dt} \left(uu^* \right)= u_{t}u^*+uu_{t}^*.
		\end{equation}

		According to Schr\"{o}dinger's equation:
		\[-\mathrm{i}hu_{t}=\frac{h^2}{2m}\triangle u+ \frac{e^2}{r}u,\]
		we will obtain that
		\begin{equation*}
			\begin{cases}
				u_{t}=\frac{\mathrm{i}h}{2m}\triangle u+ \frac{\mathrm{i}e^2}{hr}u,
				\\
				u_{t}^*=-\frac{\mathrm{i}h}{2m}\triangle u^*-\frac{\mathrm{i}e^2}{hr}u^*,
			\end{cases}
		\end{equation*}

		Therefore,

		\begin{align} \label{derivative_plus_schrodinger}
				u_{t}u^*+uu_{t}^*&=\left(\frac{\mathrm{i}h}{2m}\triangle u+\frac{\mathrm{i}e^2}{hr}u\right)u^*-u\left(\frac{\mathrm{i}h}{2m}\triangle u^*+\frac{\mathrm{i}e^2}{hr}u^*\right) \nonumber \\
			&= \frac{\mathrm{i}h}{2m}(u^*\triangle u -u\triangle u^*).
			\end{align}

		We also have:
		\begin{align} \label{laplacian_as_dot_w_gradient}
		\triangle u \cdot u^*-u\cdot\triangle u^*&= \triangle u \cdot u^*+ \nabla u\cdot \nabla u^*- \nabla u\cdot \nabla u^*- u\cdot\triangle u^* \nonumber \\
		&=\nabla \cdot (\nabla u \cdot u^* -u\cdot \nabla u^*),
		\end{align}
		putting together (\ref{d|u|^2/dt}), (\ref{derivative_plus_schrodinger}) and (\ref{laplacian_as_dot_w_gradient}) we have:
	\begin{align*}
		\frac{d}{dt}\left | u \right |^2 =\frac{\mathrm{i}h}{2m}\nabla \cdot (\nabla u \cdot u^* -u\cdot \nabla u^*).
	\end{align*}

	Then:
	\[
		\frac{d}{dt}\int \left | u \right |^2d\vec{x} = \int \left(\frac{d}{dt}\left | u \right |^2\right)d\vec{x} =\frac{\mathrm{i}h}{2m}\int\nabla \cdot (\nabla u \cdot u^* -u\cdot \nabla u^*)d\vec{x},
	\]
	So in order to prove $\frac{d}{dt}\int|u|^2d\vec{x}=0$ it sufices to show that:
	\[
		\int\nabla \cdot (\nabla u \cdot u^* -u\cdot \nabla u^*)d\vec{x}=0.
	\]
            In $\mathrm{R}^3$ space, let $B(r)$ be a ball centered at the origin with radius $r$.
		Then
		\[
			\int\nabla \cdot (\nabla u \cdot u^* -u\cdot \nabla u^*)d\vec{x} = \lim_{r \to \infty}\int_{B(r)}\nabla \cdot (\nabla u \cdot u^* -u\cdot \nabla u^*)d\vec{x}.
		\]
			From the divergence theorem,
			\[\int_{B(r)} \nabla \cdot (\nabla u \cdot u^* -u\cdot \nabla u^*)d\vec{x}= \int_{\partial B(r)}^{}(\nabla u \cdot u^* -u\cdot \nabla u^*) \cdot \bar{n} dS.	\]
			Assume that $u \to 0$ and $\nabla u \to 0$ fast enough as $\left | \vec{x} \right | \to \infty$, then we get
		
		\[ \lim_{r \to \infty}\int_{B(r)}^{} \nabla \cdot (\nabla u \cdot u^* -u\cdot \nabla u^*)d \vec{x } =0,\]
		which is what we wanted to prove.

		In conclusion: at all later times, $ \int \left | u^2 \right | d \vec{x } =1$.
		
\section{Strauss section 1.4}
\subsection{Exercise 1}
By trial and error, find a solution of the diffusion equation $u_t=u_{xx}$ with the initial condition $u(x,0)=x^2.$
		
\textbf{Solution:}

From the initial condition $u(x,0)=x^2$, we know that $u_{xx}=2=u_t$.
		
		Then, integral $u_{t}$ about $t$, we obtain that $\int u_{t} dt= \int 2 dt = 2t$,

		Therefore, we can construct $u(t,x)=x^2+2t$.

		Let's check it, since $u_{t}=2, u_{xx}=2$,

		\[u_{t}-u_{xx}=2-2=0,\] and it also satisfies the initial condition: $u(x,0)=x^2$, hence, a solution is $u(t,x)=x^2+2t$.

		\subsection{Exercise 2}
		\subsubsection{}
		Show that the temperature of a metal rod,
			insulated at the end $x=0$, satisfies the boundary
			condition $\frac{\partial u}{\partial x} =0$. (Use
		Fourier's law.)

		\textbf{Solution:}

			By Fourier's law we have:
			\[
				H_t = ku_x
			\]
			The rod being insulated at $x=0$ means that there is no
			heat exchange at that point, so we have:
			\[
				0 = H_t(0,t) = ku_x(0,t) \implies u_x(0,t) =0
			\]
			This shows what we wanted, namely that the temperature
			satisfies the boundary condition:
			\[
				\frac{\partial u}{\partial x} =0.
			\]
		\subsubsection{}
		Do the same for the diffusion of gas along a tube that is closed off at the end $x=0$. (Use Fick's law.)
		
		\textbf{Solution:}
			By Ficks's law we have:
			\[
				M_t = ku_x
			\]
			The tube being closed off at the $x=0$ means that there is no
			change in the mass of gas at that point, so we have:
			\[
				0 = M_t(0,t) = ku_x(0,t) \implies u_x(0,t) =0
			\]
			This shows what we wanted, namely that the concentration
			satisfies the boundary condition:
			\[
				\frac{\partial u}{\partial x} =0.
			\]
	\subsubsection{}
Show that the three-dimensional version of (a) (insulated solid) or (b) (impermeable container) leads to the boundary condition $\partial u/ \partial n=0$.
		
\textbf{Solution:}

We will choose (a) insulated solid to show the boundary condition in the three-dimensional version.
	    
Assume $D$ is an insulated solid and let $\vec{n}$ be the unit normal vector on $\partial D$.
By Fourier's law, we have
\[
H_{t}= k \nabla u,
\]
which implies
\[
	\vec{n}\cdot H_{t}= k \vec{n}\cdot\nabla u.
\]
Since $D$ is insulated there cannot
be exchage of heat in the direction of $\vec{n}$, otherwise there would be heat
flowing in or out of the boundary.

Now let $x_b$ be any point on $\partial D$. By the explanation above we see that:
\[
	0=(\vec{n}\cdot H_t)(x_b,t)=(k \vec{n}\cdot\nabla u)(x_b,t)
\]
Given that $k\neq 0$ and because $\vec{n}\cdot \nabla u=\partial u /\partial n$
we conclude that for any point on $\partial D$ the boundary condition
$\partial u/\partial n=0$ is satisfied.

\section{Strauss section 1.5}
\subsection{Exercise 1}
Consider the problem
		\begin{equation*}
			\begin{cases}
				\frac{d^2u}{dx^2}+u = 0,
				\\
				u(0)=0 \text{ and } u(L)=0.
			\end{cases}
		\end{equation*}
		consisting of an ODE and a pair of boundary
		conditions. Clearly, the function $u(x) \equiv 0$ is a
		solution. Is the solution \textit{unique}, or \textit{not}?
	Does the answer depend on L?

	\textbf{Solution:}

		We saw how to solve these equations in class.
		The characteristic equation is:
		\[
			\lambda^2 +1=0
		\]
		So the solution is:
		%\begin{align*}
		%	u = d_1e^{ix} + d_2e^{-ix} \\
		%	u = c_1\text{cos}x +
		%	c_2\text{sin}x
		%\end{align*}
% I want to merge them
\[u = d_1e^{ix} + d_2e^{-ix} =u = c_1\text{cos}x +	c_2\text{sin}x.\]
		Now we use the first boundary condition:
		\[
			u(0)=0 \iff c_1\text{cos}(0) +
			c_2\text{sin}(0) = 0 \implies c_1=0,
	        \]
		so the solution is of the form:
		\[
			u(x)=c_{2}\text{sin}x.
		\]
		Using the second boundary condition we get:
		\[
			u(L)=0 \iff c_{2}\text{sin}(L) =0 \implies c_{2}=0 \text{ or } L=k\pi, k\in \mathrm{Z}.
		\]
		Now we see that the answer depends on $L$. If $L$ is of the form $k\pi$ where $k$ is an integer, then $c$ can be anything, so we have infinite solutions.

		In the case that $L$ is not of the above form, we need $c=0$
		in order to satisfy the boundary condition, so in
		this case we have a unique solution, which is $u
		\equiv 0$.
		
		\subsection{Exercise 4}
		Consider the Neumann problem
		\begin{equation*}
			\begin{cases}
				\triangle u = f(x,y,z), \text{ in D, }
				\\
				\frac{\partial u}{\partial n}=0, \text{ on bdy D. }
			\end{cases}
		\end{equation*}
	
		\subsubsection{}
		What can we surely add to any
		solution to get another solution? So we
	don't have uniqueness.

	\textbf{Solution:}

		We can add a constant, because if $u$ is a solution,
		then,
		\begin{equation*}
			\begin{cases}
			\Delta(u+c)= \Delta u,
             \\
			 \frac{\partial(u+c)}{\partial n}=\frac{\partial u}{\partial n}.
			\end{cases}
		\end{equation*}
		
		So $u+c$ is also a solution.

	\subsubsection{}
	Use the divergence theorem and the PDE to show that
\[
\iiint\limits_{D}^{} f(x,y,z)dxdydz=0
\]
	is a necessary condition for the Neumann problem to have a solution.
		
	\textbf{Solution:}

	Integrating $\triangle u = f(x,y,z)$ in D, we obtain
		\[0= \iiint\limits_{D}^{} f(x,y,z)dxdydz=\iiint\limits_{D}^{} \triangle u dxdydz=\iiint\limits_{D}^{} \nabla \cdot \nabla u dxdydz
		\]
		From divergence theorem,
		\[\iiint\limits_{D}^{} \nabla \cdot \nabla u dxdydz=\iint_{S}^{} \nabla u \cdot \vec{n}dS=\iint_{S}^{} \frac{\partial u}{\partial n}dS,
			\]

			Therefore, if we want to have a solution of the Neumann problem, we have to satisfy the boundary condition, which also means $ \iiint\limits_{D}^{} f(x,y,z)dxdydz=0$ is a necessary condition for the Neumann problem to have a solution.
		\subsubsection{}
	Can you give a physical interpretation of part (a) and/or (b) for either heat flow or diffusion?
		
	\textbf{Solution:}

	We will consider heat flow at first. For heat flow, \[f(x,y,z)=ku_{t},\]
		where $k$ is a proportionality factor (the "heat conductivity"), $u(t,x)$ is the temperature.
        
		Since in $D$, \[\triangle u = f(x,y,z),\] function $f$ doesn't contain variable $t$, this means the equation is independent to $t$, which shows that the heat flow won't change with time goes by, therefore, if there is a heat source $f(x,y,z)$, the heat flow of this system will be steady at any time. 
		
		Also from Fourier's law, heat flows from hot to cold regions proportionately to the temperature gradient, therefore, the heat flow would only depend on the region of temperature.
         
		For (a), when we increase a certain temperature everywhere, the system is still stable, which means heat flow is the same as before. 

		Also, for (b), the Neumann boundary condition means that the whole system is insulated. From Fourier's theorem, it also means that there are no heat flow out and flow in at the boundary, therefore, heat won't be loss from $D$ with time changes.

		Then we consider diffusion, similar, $f(x,y,z)=ku_{t},$ where $k$ is a proportionality constant, but from here, $u(t,x)$ means the concentration of object.
		
		For (a), the diffusion of object won't change if add a certain mass everywhere. And the diffusion only depends on the difference of different concentration regions.

		For (b), since Neumann problem is achieved, on the boundary D, there are no mass flow in or flow out, therefore, this is a closed off system, and the mass $M(t)$ won't change with time goes by.  

\end{document}
